Investigating the Applications and Limits of Single asymmetric Particle Light Scattering using Limited Detection Schemes

### 2022-11-10 Manuscript.tex
Add files via upload

As can be seen from \figurename{ 2}, the dimer undergoes a full $180^{\circ}$ rotation upon entering the trap. Typically horizontal alignment of a dimer is unstable and will result in the particle rotating to align along its vertical axis. It is interesting to note that the dimer is furthest from the trap centre as it goes into a horizontal orientation before drawing closer again as it inverts completely. Further simulations of differently sized dimers showed similar results, but only when $a_1 \geq 2a_2$. Dimers with more symmetrical size ratios immediately aligned into a fixed vertical position. 
In Vigilante's work with dimers \cite{Vigilante2020Brownian_OT} simulations of trapped symmetrical dimers was investigated; their findings showed that the optical torque on the dimer goes to zero while aligned vertically and is at its maximum in a horizontal alignment. Therefore, the inversion of an asymmetric dimer suggests that if the size difference is significant the optical torque goes is minimal for a dimer in both horizontal and vertical orientations. Once we have our experimental set up complete we can confirm this by trapping an asymmetric dimer and monitoring its orientation.

\newpage
\subsection{Predictive efficacy of model}
\label{sec:3.2}
The data from \figurename{ 2a} was used to test the efficacy of our predictive model. To visualise how well our model tracks the dimer's orientation we plot the radial distance between our model's prediction and the true orientation, and between the best possible orientation and the true orientation. For a perfect estimation these two plots should overlap. Overall their our three main factors that effect the performance of our prediction; the signal error $\sigma$, our choice of angles $\theta_1, \theta_2, \ \& \theta_3$, and our weighting factor $\beta$.

We tested how changing our weighting factor for a set choice of angles would influence the performance of our model.  We first set our choice of angles to $15^{\circ}, \ 45^{\circ},\ \& \ 90^{\circ}$ and varied $\beta$ between 0.5-1.5.

@@

As covered in \ref{sec:3.2} our choice for beta can help to improve our estimation somewhat by limiting our estimation in the physical space.

\section{Conclusion}
\label{4}
We have developed a model for interpreting the dynamics of a trapped particle based purely on the light scattering pattern. Compared to a random selection of the particle's orientation we find that our model has a $150\%$ increase in it's accuracy. Even more interestingly, our model performs better under noisy signal conditions by allowing our estimate to self-correct itself, in the future we hope to remove the artefacts of the signal noise by combing multiple estimates using different detection angles. This can be achieved via the inclusion of additional signal detections, we refrained from collecting more signal point for two key reasons; firstly, we wanted to show the extent of the mathematical model in the case of limited detection schemes, and secondly, we wanted to limit our model to what is possible in a real world experimental set up. Once we have a clearer understanding of the maximum limit of detection fibres that can be placed we can update our model to account for this and improve the accuracy further.

>>>>

As can be seen from \figurename{ 2}, the dimer undergoes a full $180^{\circ}$ rotation upon entering the trap. Typically horizontal alignment of a dimer is unstable and will result in the particle rotating to align along its vertical axis. It is interesting to note that the dimer is furthest from the trap centre as it goes into a horizontal orientation before drawing closer again as it inverts completely. Further simulations of differently sized dimers showed similar results, but only when $a_1 \geq 2a_2$. Dimers with more symmetrical size ratios immediately aligned into a fixed vertical position. 
In Vigilante's work with dimers \cite{Vigilante2020Brownian_OT} simulations of trapped symmetrical dimers was investigated; their findings showed that the optical torque on the dimer goes to zero while aligned vertically and is at its maximum in a horizontal alignment. Therefore, the inversion of an asymmetric dimer suggests that if the size difference is significant the optical torque goes is minimal for a dimer in both horizontal and vertical orientations. Once we have our experimental set up complete we can confirm this by trapping an asymmetric dimer and monitoring its orientation. The data from \figurename{ 2a} was used to test the efficacy of our predictive model. To visualise how well our model tracks the dimer's orientation we plot the radial distance between our model's prediction and the true orientation, and between the best possible orientation and the true orientation. For a perfect estimation these two plots should overlap, while  we cannot achieve an exact estimation there are several parameters that will effect our model's efficacy.

\newpage
\subsection{Predictive efficacy of model}
\label{sec:3.2}
When we choose our three detction angles we are also inherently setting the lower limit for our signal error based on the minimum spacing between our $y_k$ values. If then signal error is smaller than this minimum distance then every refernce orientation will have the same probability $p(\hat{n} \parallel y_k)$ resulting in our model performing worse than just assigning reference orientations at random. We can reduce this minimum distance by creating more reference orientations thus increasing the accuracy of our predictive model. However if our signal error is to large then we are limited in how many refernece orienations we can use; futhermore, if the signal error is to large then our prediction can be.

@@

As covered in \ref{sec:3.2} our choice for beta can help to improve our estimation by restricting it in the physical space. By tuning our choices of $\beta$ in accordance with

\section{Conclusion}
\label{4}
We have developed a model for interpreting the dynamics of a trapped particle based purely on the light scattering pattern.
